\documentclass[11pt]{article}

\usepackage{bm}
\usepackage{enumerate}
\usepackage{etaremune}
% \usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}

\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{2in}

% For links of references
\hypersetup{colorlinks,
  linkcolor=blue,
  filecolor=blue,
  urlcolor=blue,
  citecolor=blue}

\newcommand\technical[2]{
  \noindent
%  \begin{minipage}{0.03\linewidth}
%    \null
%  \end{minipage}
%  \begin{minipage}{0.97\linewidth}
    {\large\bf #1:} #2\\
%  \end{minipage}\\
  }

\newcommand\sectitle[1]{
  \vspace{0.5cm}
  \noindent
  \textbf{\large #1}\\
  \vspace{-0.2cm}
}

\newcommand\email[1]{\href{mailto:#1}{\texttt{#1}}}


\begin{document}

% \begin{figure}[t]
\begin{minipage}[b]{0.46\linewidth}
\flushleft
% \noindent
\hspace{-0.7cm}
{\bf\huge Crist\'obal Sif\'on}\\\vspace{0.2cm}
\hspace{-0.5cm}{\large Postdoctoral Research Associate\\
\hspace{-0.65cm}        Department of Astrophysical Sciences\\
\hspace{-0.65cm}        Princeton University\\
\hspace{-0.65cm}        Peyton Hall, 4 Ivy Ln, Princeton, NJ 08544}\\
\end{minipage}
\begin{minipage}[b]{0.49\linewidth}
\flushright
{\large E-mail: {\texttt sifon@astro.princeton.edu}\\
        Phone: +1 609 258 0026\\
        \url{http://www.astro.princeton.edu/~sifon/}
        \url{https://github.com/cristobal-sifon/}}
\end{minipage}
\vspace{0.4cm}
\hline


\sectitle{Research Interests}

%{\large
I am an observational astrophysicist. My research focuses on galaxy 
cluster physics including observable--mass scaling relations for cosmological 
analyses, brightest cluster galaxies, the mass content of cluster galaxies and 
diffuse radio emission. I am also interested in intrinsic galaxy alignments, both 
as contaminants for cosmic shear and as a physical mechanism in its own right. I 
use various tools and techniques to study these phenomena, including weak 
gravitational lensing, spectroscopy, and the exploitation of optical surveys in 
general. I have presented my work at various conferences, workshops and seminars 
in Chile, Europe and the US.

\vspace{0.5cm}
\technical{Collaborations}
{Atacama Cosmology Telescope (ACT), Canadian Cluster Comparison Project (CCCP), 
Kilo-Degree Survey (KiDS), Hyper-Suprime Cam survey (HSC), Large Synoptic Survey Telescope Dark Energy Science Collaboration (LSST-DESC),
Multi-Epoch Nearby Cluster Survey (MENeaCS).}


\vspace{-0.5cm}
\sectitle{Employment and Education}

\noindent
\emph{2016 --- Present} -- Postdoctoral Research Associate, Princeton University, USA\\
\emph{2016} -- Ph.D.~Astrophysics, Universiteit Leiden, The Netherlands\\
\emph{2012} -- M.Sc.~Astrophysics, P.~Universidad Cat\'olica de Chile, Chile\\
\emph{2010} -- B.Sc.~Astronomy, P.~Universidad Cat\'olica de Chile, Chile


%\vspace{0.5cm}
%\technical{Student Mentoring Experience}

%{I am mentoring a PhD student from Oxford University (UK) working with Prof.\ Joanna Dunkley on weak lensing calibration of the total masses of galaxy clusters selected with the Sunyaev-Zel'dovich effect by the Atacama Cosmology Telescope, using the Kilo-Degree Survey, since the second semester of 2017. I will also mentor a Princeton undergraduate for a summer research project during June-August 2018 looking at cluster galaxy alignments with the Hyper Suprime-Cam survey.}

%\vspace{-0.5cm}
\sectitle{Student Mentoring}

\noindent
\emph{2018} -- Undegraduate Summer Research Program, Princeton University\\
\emph{2017 --- Present} -- Naomi Robertson, PhD student, Oxford University (UK). Mentoring one of her thesis projects combining data from ACT and KiDS.


%\vspace{-0.5cm}
\sectitle{Successful Observing Proposals (as PI)}

\noindent
\emph{Gemini-South Telescope} -- 24 h for imaging and spectroscopy of massive 
high-redshift galaxy clusters\\
\emph{Giant Metrewave Radio Telescope} -- 44 h to search for diffuse radio 
emission in massive galaxy clusters\\
\emph{VLT Survey Telescope} -- 6 h for weak lensing observations of a massive 
galaxy cluster\\


\technical{Observing Experience}
{I have spent roughly 180 hours observing in 
optical (Gemini-South) and near-infrared (ESO-NTT) telescopes performing both 
imaging and spectroscopy of galaxy clusters.}\\

\vspace{-0.5cm}
\technical{Technical skills}
{I am an experienced \texttt{python} programmer, and I also have some experience 
with IRAF/PyRAF. I have written {\tt pygmos}, a Python/PyRAF pipeline to reduce 
Gemini-GMOS spectra which is available 
\href{https://github.com/cristobal-sifon/pygmos/}{\texttt{here}}. Other codes I 
have written are posted at my 
\href{https://github.com/cristobal-sifon}{\texttt{github}} page.}


%\sectitle{Language skills}
%
%{Native Spanish, fluent English, basic Dutch}

\technical{Community Activity}
{I have served as a referee for A\&A, ApJ, and Nature Astronomy.}


\pagebreak
%\vspace{-0.5cm}
\sectitle{Teaching Assistant Experience}

\noindent
\emph{2013-B} -- Stellar Dynamics (Leiden, Prof.~S.~Portegies Zwart)\\
\emph{2012-A} -- Extragalactic Astrophysics (PUC, Prof.~L.~F.~Barrientos)\\
\emph{2011-A} -- Extragalactic Astrophysics (PUC, Prof.~L.~F.~Barrientos)\\
\emph{2011-A} -- Laboratory of Thermodynamics and Kinetic Theory (PUC, Prof.~U.~Volkmann)\\
\emph{2010-B} -- Experimental Astrophysics (PUC, Prof.~L.~F.~Barrientos)


\sectitle{Other Work Experience}

\noindent
\emph{2007 --- 2008} -- Ski instructor at Homewood Mountain Ski Resort in Lake Tahoe, CA. Obtained the certification as Level I ski instructor  by the Professional Ski Instructors of America (PSIA).\\
\emph{2006 --- 2007} -- Lift operator at Sun Valley Resort, Sun Valley, ID.

\vspace{1cm}
\hline
\vspace{1cm}

\noindent
{\bf\Large References}
% \vspace{-0.6cm}
\begin{itemize}
%  \item 
 \item Prof.~Henk Hoekstra (\textit{PhD advisor})\\
       Leiden Observatory\\
       Universiteit Leiden\\
       Niels Bohrweg 2, NL-2333 CA Leiden, The Netherlands\\
       Phone: +31 (71) 527 5594\\
       E-mail: \email{hoekstra@strw.leidenuniv.nl}
 \item Prof.~David N.~Spergel\\
       Department of Astrophysical Sciences\\
       Princeton University\\
       4 Ivy Ln, Princeton, NJ 08544, USA\\
       Phone: +1 (609) 258 3589\\
       E-mail: \email{dns@astro.princeton.edu}
 \item Prof.~John P.~Hughes\\
       Department of Physics and Astronomy\\
       Rutgers University\\
       136 Frelinghuysen Rd., Piscataway, NJ 08854, USA\\
       Phone: +1 (848) 445 8878\\
       E-mail: \email{jph@physics.rutgers.edu}
% \item Prof.~L.~Felipe Barrientos (\textit{MSc advisor})\\
%       Departamento de Astronom\'ia y Astrof\'isica\\
%       P. Universidad Cat\'olica de Chile\\
%       Casilla 306, Santiago 22, Chile\\
%       E-mail: \email{barrientos@astro.uc.cl}
% \item Dr.~Felipe Menanteau\\
%       Department of Astronomy\\
%       University of Illinois at Urbana-Champaign\\
%       1002 W.\ Green St., Urbana, IL 61801, USA\\
%       E-mail: \email{felipe@illinois.edu}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% PUBLICATION LIST %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Uncomment these two lines to get the publication list in the main pdf

% \pagebreak
% \input{Sifon_publications}

\end{document}
